working title Compatibility system and stigma size are the main predictors of heterospecific pollen effect

### 2019-03-13 Manuscript_draft/Manuscript_draft.Rmd
progressing with the draft. Analysis.

>>>>

To compare the magnitude of effect of heterospecific pollen across species we conducted standarized Hedges' d [(mean of mixed 50% mix - mean of cross pollination)/pooled SD]. We did in three different ways: effect sizes of each donor per focal species; effect sizes per family of the different donors per focal species; effect sizes of all the donors grouped per focal species.

### 2019-03-13 Manuscript_draft/Manuscript_draft.tex
progressing with the draft. Analysis.

>>>>

To compare the magnitude of effect of heterospecific pollen across
species we conducted standarized Hedges' d {[}(mean of mixed 50\% mix -
mean of cross pollination)/pooled SD{]}. We did in three different ways:
effect sizes of each donor per focal species; effect sizes per family of
the different donors per focal species; effect sizes of all the donors
grouped per focal species.
